Approximation as Differentiation

### 2025-07-08 main/models.tex
Standardise on 'cartesian'.

We have constructed the category
$\Fam(\MeetSLat \times \JoinSLat^\op)$, which is a cartesian closed
category with all coproducts, ienough to interpret the total
higher-order language we define in the next section with primitive
types and operations defined in $\Fam(\LatGal)$. However, we are not
guaranteed by construction that at first-order type, the
interpretations are in fact Galois connections. We will rectify this
in \secref{definability} using a logical relations construction.

@@

Comparing this conjecture to the previous one, we can see that the
difference between $\CM$, $\Lposet$ and $\Fam(\MeetSLat)$,
$\Fam(\LatGal)$ is that the latter have a separation of points from
tangents, somewhat analogous to the situation with manifolds. Also
note that, contrary to the $\Fam(\FinVect)$ representation of
manifolds and differentiable maps, (if this conjecture holds) we do
not throw away information about higher derivatives. It is retained in
the order structure of the tangent fibres.

>>>>

We have constructed the category
$\Fam(\MeetSLat \times \JoinSLat^\op)$, which is a cartesian closed
category with all coproducts, enough to interpret the total
higher-order language we define in the next section with primitive
types and operations defined in $\Fam(\LatGal)$. However, we are not
guaranteed by construction that at first-order type, the
interpretations are in fact Galois connections. We will rectify this
in \secref{definability} using a logical relations construction.

@@

Comparing this conjecture to the previous one, we can see that the
difference between $\CM$, $\Lposet$ and $\Fam(\MeetSLat)$,
$\Fam(\LatGal)$ is that the latter have a separation of points from
tangents, somewhat analogous to the situation with manifolds. Also
note that, if this conjecture holds, then contrary to the $\Fam(\FinVect)$ representation of
manifolds and differentiable maps, we do
not throw away information about higher derivatives. It is retained in
the order structure of the tangent fibres.

### 2025-07-08 main/related-work.tex
Standardise on 'cartesian'.

\emph{Tangent categories}, due originally to \citet{rosický84} and developed by \citet{cockett14,cockett18},
provide an abstract categorical framework for reasoning about differentiation, inspired by the structure of
the tangent bundle in differential geometry. In a tangent category, each object $X$ is equipped with a tangent
bundle $T(X)$, and each morphism $f: X \to Y$ has a corresponding differential map $T(f): TX \to TY$
satisfying axioms analogous to the chain rule and linearity of differentiation. Tangent categories generalise
Cartesian differential categories \cite{cdcs}, which model differentiation over Cartesian closed categories
using a syntactic derivative operator. The motivation behind tangent categories is to \roly{Bob to say
something here..}

>>>>

\emph{Tangent categories}, due originally to \citet{rosický84} and developed by \citet{cockett14,cockett18},
provide an abstract categorical framework for reasoning about differentiation, inspired by the structure of
the tangent bundle in differential geometry. In a tangent category, each object $X$ is equipped with a tangent
bundle $T(X)$, and each morphism $f: X \to Y$ has a corresponding differential map $T(f): TX \to TY$
satisfying axioms analogous to the chain rule and linearity of differentiation. Tangent categories generalise
Cartesian differential categories \cite{cdcs}, which model differentiation over cartesian closed categories
using a syntactic derivative operator. The motivation behind tangent categories is to \roly{Bob to say
something here..}
